---
title: "Paper_stuff"
output: html_document
date: "2023-09-12"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Libraries
library(tidyverse)
library(dplyr)
library(haven)
library(ggplot2)
library(tidyr)
```

# Import data

Read in the dataset. 
```{r}
Mothership <- read_sav("~/Desktop/Coding/data/PHPoutcome_clean.sav")
View(df)
```

## Rename and Recode variables 
We can change the current variables to make them easier to interpret. 
```{r}
#recode varaibles
Mothership <- mutate(Mothership, 
                     DC_status_1 = as.factor(DC_status_1),
                     DC_status_1 = recode(DC_status_1,
                                          "1"="Complete",
                                          "2"="Nearly Complete",
                                          "3"="Insurance",
                                          "4"="Nonatteneance",
                                          "5"="Inappropriate",
                                          "6"="Inpatient",
                                          "7"="Withdrew",
                                          "8"="Dissatisfaction",
                                          "9"="Other"),
                     Education_1 = as.factor(Education_1),
                     Education_1 = recode(Education_1,
                                          "1"="<Grade 12",
                                          "2"="HS Diploma",
                                          "3"="GED",
                                          "4"="Some College",
                                          "5"="Associates Degree",
                                          "6"="Bachelors Degree",
                                          "7"="Some Grad School",
                                          "8"="Grad Degree"),
                     Gender_1 = as.factor(Gender_1),
                     Gender_1 = recode(Gender_1,
                                       "0"="Female",
                                       "1"="Male",
                                       "2"="Non-Binary",
                                       "3"="Other",
                                       "4"="Unknown"),
                     Relationship_1 = as.factor(Relationship_1),
                     Relationship_1 = recode(Relationship_1,
                                             "0"="Married",
                                             "1"="Cohabitating",
                                             "2"="Widowed",
                                             "3"="Separated",
                                             "4"="Divorced",
                                             "5"="Never Married"),
                     Sexuality_1 = as.factor(Sexuality_1),
                     Sexuality_1 = recode(Sexuality_1,
                                          "1"="Straight",
                                          "2"="Gay",
                                          "3"="Bisexual",
                                          "4"="Other"),
                     IPT_track_1 = as.factor(IPT_track_1),
                     IPT_track_1 = recode(IPT_track_1,
                                          "0"="General",
                                          "1"="Trauma",
                                          "2"="Young Adult",
                                          "3"="BPD"),
                     Race_1 = as.factor(Race_1),
                     Race_1 = recode(Race_1,
                                     "0"="White",
                                     "1"="Black",
                                     "2"="Hispanic",
                                     "3"="Asian",
                                     "4"="Portugese",
                                     "5"="Other"),
                     Education_1 = as.factor(Education_1),
                     Education_1 = recode(Education_1,
                                      "0"="<Grade 6", 
                                      "1"="Grades 7-12",
                                      "2"="HS Diploma", 
                                      "3"="GED",
                                      "4"="Some College",
                                      "5"="Associates Degree",
                                      "6"="Bachelors Degree",
                                      "7"="Some Grad School",
                                      "8"="Grad Degree"),
                     DC_status_1 = as.factor(DC_status_1),
                     DC_status_1 = recode(DC_status_1,
                                      "1"="Treatment Complete",
                                      "2"="Treatment Near Complete",
                                      "3"="Insurance Stopped",
                                      "4"="Nonattendence",
                                      "5"="Inapproparite Language",
                                      "6"="Transfered To Impatient",
                                      "7"="Withdrew for External factors",
                                      "8"="Withdrew (AMA)",
                                      "9"="Other",
                                      "10"="Other"),
                    DC_status_1 = as.factor(DC_status_1),
                    DC_status_1 = recode(DC_status_1,
                                      "1"="Inpatient",
                                      "2"="PHP",
                                      "3"="APS",
                                      "4"="Psychatrist",
                                      "5"="PCP",
                                      "6"="Another Physican",
                                      "7"="Therapist",
                                      "17"="Other"
                    ),
                                        
#Lets make some new variables 
      #Duration of treatment
                     Duration = as.factor(
                       ifelse(Days_complete_1>0 & Days_complete_1 <=5, "1",
                       ifelse(Days_complete_1>5 & Days_complete_1 <=10, "2",
                       ifelse(Days_complete_1>10 & Days_complete_1 <=15, "3",
                       ifelse(is.na(Days_complete_1), NA, "4"
                              ))))),
                    Duration = as.factor(recode(Duration,
                                      "1"="1-5",
                                      "2"="6-10",
                                      "3"="11-15",
                                      "4"="16+"
                                      )))
    

#Extract Year From Intake Date
#Convert to Date
library("lubridate")
Mothership$Intake_1<-ymd(Mothership$Intake_1)
Mothership$TxYear<-as.numeric(format(Mothership$Intake_1,"%Y"))
Mothership<-mutate(Mothership,
                   TxYear = as.factor(TxYear),
                   TxYear = recode(TxYear,
                                   "1582"="2014"))
```


## Export as CSV
```{r}
write.csv(Mothership,"~/Desktop/Coding/data/Mothership_paper")
```


```{r}
Mothership<-Mothership %>%
  mutate(
          # Mood Disorders
                     Mood_D = as.factor(
                      ifelse(
                        MDD_P ==1 | Bipolar1_P == 1 | Bipolar2_P == 1 | Dysthymia_P == 1, 1, 0)),
          # Anxiety Disorders
                    Anxiety_D = as.factor(
                      ifelse(
                        GAD_P ==1 | Panic_P == 1 | PanicAgor_P == 1 | Agoraphobia_P == 1 |
                        Social_P == 1 | Specific_P == 1, 1, 0)),
          # Obsessive Compusive Disorders
                #OCD_P is for current OCD
                OCD_P = as.factor(OCD_P),
          # Personality Disorders
                #BPD_P is for current BPD
                BPD_P = as.factor(BPD_P),
          # Substance Use Disorders
                    Substance_D = as.factor(
                      ifelse(
                        Alcohol_P == 1 | Drug_P ==1, 1, 0)),
          # Trauma or stresor related disorders
                    Trauma_D = as.factor(
                      ifelse(PTSD_P == 1 | Adjustment_P ==1, 1,0)),
          # Psychotic Disorders
                    Psychotic_D = as.factor(
                      ifelse(
                        Schiz_P == 1 | Schizaff_P == 1,1,0)),
            # Eating Disorders
                    Eating_D = as.factor(
                      ifelse(
                        Anorex_P == 1 | Bulim_P == 1 | Binge_P == 1, 1,0)),
            # Somatic Disroders
                    Somatic_D = as.factor(
                      ifelse(
                        Somat_P == 1 | UndiffSoma_P == 1| Hypochondriasis_P ==1,
                        1,0)),
                    Other = as.factor(
                        ifelse(
                        Somat_P == 1 | UndiffSoma_P == 1| Hypochondriasis_P ==1 |
                        Anorex_P == 1 | Bulim_P == 1 | Binge_P == 1 | Schiz_P == 1 | 
                        Schizaff_P == 1 | Alcohol_P == 1 | Drug_P ==1 | OCD_P ==1,
                        1,0)),
                    Disorder_Type = as.factor(
                      ifelse(Anxiety_D == 1, "Anxiety",
                      ifelse(OCD_P == 1, "OCD",
                      ifelse(BPD_P == 1, "BPD",
                      ifelse(Substance_D == 1, "Substance Use",
                      ifelse(Trauma_D == 1, "Trauma",
                      ifelse(Mood_D == 1, "Mood",
                      ifelse(Psychotic_D == 1, "Psychotic", 
                      ifelse(Eating_D == 1, "Eating", 
                      ifelse(Somatic_D == 1, "Somatic", NA
                      )))))))))),
                    Disorder_treat = as.factor(
                      ifelse(Anxiety_D == 1, "Anxiety",
                      ifelse(BPD_P == 1, "BPD",
                      ifelse(Trauma_D == 1, "Trauma",
                      ifelse(Mood_D == 1, "Mood",
                      ifelse(OCD_P == 1, "Other",
                      ifelse(Substance_D == 1, "Other",
                      ifelse(Psychotic_D == 1, "Other", 
                      ifelse(Eating_D == 1, "Other", NA
                      ))))))))),
                  Anxiety_C =  as.factor(
                    ifelse( GAD_P !=1 & GAD_C ==1 | 
                        Panic_P != 1 & Panic_C == 1 | 
                        PanicAgor_P != 1 & PanicAgor_C == 1 | 
                        Agoraphobia_P != 1 & Agoraphobia_C == 1 |
                        Social_P != 1 & Social_C == 1 | 
                        Specific_P != 1 & Specific_C == 1, 1, 0)),
                  Mood_C =  as.factor(
                    ifelse( MDD_P != 1 & MDD_C == 1 |
                        Bipolar1_P != 1 & Bipolar1_C == 1 | 
                        Bipolar2_P != 1 &  Bipolar2_C == 1 | 
                        Dysthymia_P != 1 & Dysthymia_C == 1 , 1, 0)),
                  Substance_C = as.factor(
                    ifelse(Alcohol_P != 1 & Alcohol_C == 1 | 
                        Drug_P != 1 & Drug_C ==1, 1, 0)),
                  Trauma_C = as.factor(
                    ifelse(PTSD_P != 1 & PTSD_C == 1 | 
                        Adjustment_P != 1 & Adjustment_C ==1, 1,0)),
                  Psychotic_C = as.factor(
                    ifelse(Schiz_P != 1 & Schiz_C == 1 | 
                        Schizaff_P != 1 & Schizaff_C == 1,1,0)),
                  Eating_C = as.factor(
                    ifelse(Anorex_P != 1 & Anorex_C == 1 | 
                        Bulim_P != 1 & Bulim_C == 1 | 
                        Binge_P != 1 & Binge_C == 1, 1,0)),
                  Somatic_C = as.factor(
                    ifelse(Somat_P != 1 & Somat_C == 1 | 
                        UndiffSoma_P != 1 & UndiffSoma_C == 1 | 
                        Hypochondriasis_P != 1 &  Hypochondriasis_C == 1, 1,0)),
                  OCD_Co_C = as.factor(
                    ifelse(OCD_P != 1 & OCD_C == 1,1,0)),
                  BPD_Co_C = as.factor(
                    ifelse(BPD_P != 1 & BPD_C ==1,1,0)),
                  No_Co = as.factor(
                    ifelse(BPD_Co_C == 0 &
                           OCD_Co_C == 0 &
                           Somatic_C == 0 & 
                           Eating_C == 0 &
                           Psychotic_C == 0 &
                           Trauma_C == 0 & 
                           Substance_C == 0 &
                           Mood_C == 0 &
                           Anxiety_C == 0, 1,0)),
                  Other_Co = as.factor(
                    ifelse(OCD_Co_C == 1 & 
                           Somatic_C == 1 & 
                           Eating_C == 1 &
                           Psychotic_C == 1,1,0)),
                  
          #emotional disorders
                  Emotional_dis = as.factor(
                    ifelse(Anxiety_D == 1 | OCD_P == 1 | Trauma_D == 1 |
                           Mood_D == 1, "Emotional Disorder", "Other Disorder")),
                 
          # co occuring disorders
                  Co_Anx = as.factor(
                        ifelse(Anxiety_C == 1 & Mood_D == 1 |
                                Anxiety_C == 1 & OCD_P == 1 |
                                Anxiety_C == 1 & BPD_P == 1 |
                                Anxiety_C == 1 & Substance_D == 1 |
                                Anxiety_C == 1 & Trauma_D == 1 |
                                Anxiety_C == 1 & Eating_D ==1 |
                                Anxiety_C == 1 & Psychotic_D ==1 |
                                Anxiety_C == 1 & Somatic_D ==1, 1, 0)),
                  Co_Mood = as.factor(
                        ifelse(Mood_C == 1 & Anxiety_D == 1 |
                                Mood_C == 1 & OCD_P == 1 |
                                Mood_C == 1 & BPD_P == 1 |
                                Mood_C == 1 & Substance_D == 1 |
                                Mood_C == 1 & Trauma_D == 1 |
                                Mood_C == 1 & Eating_D ==1 |
                                Mood_C == 1 & Psychotic_D ==1 |
                                Mood_C == 1 & Somatic_D==1 , 1, 0)),
                  Co_OCD = as.factor(
                        ifelse(OCD_C == 1 & Anxiety_D == 1 |
                                OCD_C == 1 & Mood_D == 1 |
                                OCD_C == 1 & BPD_P== 1 |
                                OCD_C == 1 & Substance_D == 1 |
                                OCD_C == 1 & Trauma_D == 1 |
                                OCD_C == 1 & Eating_D ==1 |
                                OCD_C == 1 & Psychotic_D ==1 |
                                OCD_C == 1 & Somatic_D ==1, 1, 0)),
                  Co_BPD = as.factor(
                        ifelse(BPD_C == 1 & Anxiety_D == 1 |
                                BPD_C == 1 & Mood_D == 1 |
                                BPD_C == 1 & OCD_P== 1 |
                                BPD_C == 1 & Substance_D == 1 |
                                BPD_C == 1 & Trauma_D == 1 |
                                BPD_C == 1 & Eating_D ==1 |
                                BPD_C == 1 & Psychotic_D ==1 |
                                BPD_C == 1 & Somatic_D ==1 , 1, 0)),
                  Co_Psychotic = as.factor(
                       ifelse(Psychotic_C == 1 & Mood_D == 1 |
                                Psychotic_C == 1 & OCD_P == 1 |
                                Psychotic_C == 1 & BPD_P == 1 |
                                Psychotic_C == 1 & Substance_D == 1 |
                                Psychotic_C == 1 & Trauma_D == 1 |
                                Psychotic_C == 1 & Eating_D ==1 |
                                Psychotic_C == 1 & Anxiety_D ==1 |
                                Psychotic_C == 1 & Somatic_D ==1, 1, 0)),
                  Co_Eating = as.factor(
                      ifelse(Eating_C == 1 & Mood_D == 1 |
                                Eating_C == 1 & OCD_P == 1 |
                                Eating_C == 1 & BPD_P == 1 |
                                Eating_C == 1 & Substance_D == 1 |
                                Eating_C == 1 & Trauma_D == 1 |
                                Eating_C == 1 & Psychotic_D ==1 |
                                Eating_C == 1 & Anxiety_D ==1 |
                                Eating_C == 1 & Somatic_D ==1, 1, 0)),
                  Co_Somatic =  as.factor(
                       ifelse(Somatic_C == 1 & Mood_D == 1 |
                                Somatic_C == 1 & OCD_P == 1 |
                                Somatic_C == 1 & BPD_P == 1 |
                                Somatic_C == 1 & Substance_D == 1 |
                                Somatic_C == 1 & Trauma_D == 1 |
                                Somatic_C == 1 & Eating_D ==1 |
                                Somatic_C == 1 & Anxiety_D ==1 |
                                Somatic_C == 1 & Substance_D ==1 |
                                Somatic_C == 1 & Psychotic_D ==1, 1, 0)),
                  Co_Substance = as.factor(
                      ifelse(Substance_C == 1 & Mood_D == 1 |
                                Substance_C == 1 & OCD_P == 1 |
                                Substance_C == 1 & BPD_P == 1 |
                                Substance_C == 1 & Substance_D == 1 |
                                Substance_C == 1 & Trauma_D == 1 |
                                Substance_C == 1 & Eating_D ==1 |
                                Substance_C == 1 & Anxiety_D ==1 |
                                Substance_C == 1 & Somatic_D ==1 |
                                Substance_C == 1 & Psychotic_D ==1, 1, 0)),
                 Co_Trauma = as.factor(
                    ifelse(Trauma_C == 1 & Mood_D == 1 |
                                Trauma_C == 1 & OCD_P == 1 |
                                Trauma_C == 1 & BPD_P == 1 |
                                Trauma_C == 1 & Substance_D == 1 |
                                Trauma_C == 1 & Eating_D ==1 |
                                Trauma_C == 1 & Anxiety_D ==1 |
                                Trauma_C == 1 & Somatic_D ==1 |
                                Trauma_C == 1 & Psychotic_D ==1, 1, 0))
  )
          
        
  

### Export as CSV
write.csv(Mothership,"~/Desktop/Coding/data/Mothership_Diag.csv")

##### df for plots 

# df without NAs in date and disorder type
Mothership_Diag <- Mothership %>%
  filter(!is.na(Disorder_Type))%>%
  filter(!is.na(TxYear))

Mothership_Diag_treat <- Mothership %>%
  filter(!is.na(Disorder_treat),
         !is.na(TxYear),
         !is.na(Duration)) 

# df with and without depression
No_depressy <- Mothership_Diag %>%
  filter(Disorder_Type != "Mood")
```

What Doug Wants

# Results
### The overall breakdown of patients’ demographics and diagnoses.
###	The trajectories of depression and anxiety for all patients (both numerical – pre/post scores, overall slope, and visual – graphs). Numerical results are in text, visual results presented to supplement.
- Broken down by treatment duration, treatment track, most common primary diagnoses.
###	The pre-post scores (numerical and visual) for RDQ subscales.
###	Reasons for discharge (numerical and visual).

# Visualizations
### Table – Demographics
### Table – Diagnoses
```{r}
#Demographics Table
Demo_tab_df <- Mothership_Diag_treat |>
  filter(!is.na(Education_1),
         !is.na(Race_1),
         !is.na(Gender_1),
         !is.na(Disorder_Type),
         !is.na(Relationship_1),
         
        )

Demo_tab<-data.frame(table1::table1(~Age_1+Education_1+Race_1+Gender_1+Relationship_1, data=Demo_tab_df))
colnames(Demo_tab) <- c("Variable","Total Sample")
Demo_tab

#Disorder Table
Dis_tab <- data.frame(table1::table1(~Disorder_Type | Duration, data = Mothership_Diag_treat))
colnames(Dis_tab) <- c("Primary Diagnosis","1-5 Days", "6-10 Days", "11-15 Days","16+ Days", "Total Sample")
Dis_tab
```
### Visualization – most common diagnoses.
```{r}
#frequency

ggplot(data = subset(Mothership_Diag, !is.na(Disorder_Type)),mapping = aes(x = Disorder_Type, fill=Disorder_Type))+
  geom_bar()+
  ggtitle("Frequency of Psychiatric Disorder Subtypes") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1),
        legend.position = "none")+
  xlab("Psychiatric Disorder Subtype")+
  theme(panel.grid.major.x = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,4300))+
  coord_flip()
```


```{r}
# Visualization of percent

Mothership_current_Imp <- Mothership_Diag_treat %>%
  pivot_longer(
    cols=c("Co_Anx","Co_Mood","Co_OCD","CO_BPD","CO_Psychotic","CO_Eating","CO_Somatic", "CO_Substance","CO_Trauma", "No_Co"),
    names_to = 'Disorder_Present') %>%
  filter(value != 0) %>%
  select(!value)  %>%
  filter(!is.na(Disorder_Present))%>%
  filter(!is.na(Disorder_treat)) 


co_dis_tab <- Mothership_Diag_treat |>
  pivot_longer(
    cols = c("Co_Anx","Co_Mood","Co_OCD","Co_BPD","Co_Psychotic","Co_Eating","Co_Somatic", "CO_Substance","Co_Trauma", "No_Co"),
    names_to = 'Co Occuring',
    values_to = "Number"
  ) |>
  select(Disorder_treat, `Co Occuring`, Number) |>
  filter(Number != 0,
         !is.na(`Co Occuring`),
         !is.na(Disorder_treat)) 

tabs<-as.data.frame.matrix(xtabs(~ Disorder_Present + Disorder_treat, data = Mothership_current_Imp))

anx<-summary(Mothership_Diag_treat$Anxiety_D)[2]
bpd<-summary(Mothership_Diag_treat$BPD_P)[2]
mood<-summary(Mothership_Diag_treat$Mood_D)[2]
trauma<-summary(Mothership_Diag_treat$Trauma_D)[2]
other<-summary(Mothership_Diag_treat$Other)[2]

tabs[,1] <- (tabs[,1] / anx)*100
tabs[,2] <- (tabs[,2] /bpd)*100
tabs[,3] <- (tabs[,3] /mood)*100
tabs[,4] <- (tabs[,4] /other)*100
tabs[,5] <- (tabs[,5] /trauma)*100
tabs[,6] <- c("Anxiety","BPD","Eating","Mood","OCD","Psychotic","Somatic", "Substance","Trauma", "None")
colnames(tabs)[6] = "Disorder"
tabs

CODis_tab<-data.frame(table1::table1(~`Co Occuring` | Disorder_treat, data = co_dis_tab))
CODis_tab

p <- Mothership_current_Imp %>%
  ggplot(aes(x = Disorder_treat, y = Disorder_Present, color = Disorder_treat)) +
  geom_count(aes(size = after_stat(prop),group = Disorder_treat), alpha = .75)+
 scale_size_area(max_size = 30)+
  scale_colour_manual(values = c("#FE6CAA","#f7a174","#B1D4E0","#A06CFE","red"))+
  #scale_size_continuous(range = c(10, 30)) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45,hjust = 1),
    legend.position = "none") +
  scale_y_discrete(labels=c("Other_Co" = "Other",
                            "No_Co" = "None",
                            "BPD_Co_C" = "BPD",
                            "Trauma_C" = "Trauma", 
                            "Substance_C" = "Substance Use",
                            "Mood_C" = "Mood",
                            "Anxiety_C" = "Anxiety")) +
  labs(title = "Percent of Co Occuring Psychiatric Diosrders per Primary Diagnosis",
    subtitle = "Grouped into subtypes of DSM diagonsis",
    y = "Co-Occuring Psychiatric Disorder",
    x = "Primary Psychiatric Diagnosis") 

```


•	Visualizations – CUDOS and CUXOS trajectories by treatment duration, treatment track, most common diagnoses. 
•	Visualization – RDQ pre and post change.
•	Table or Visualization – Reasons for discharge results.


# Sociodemographic Visualizations

## {.tabset}

### Education Status
```{r}
ggplot(data = subset(Mothership, !is.na(Education_1)),mapping = aes(x = Education_1))+
  geom_bar(color = "black",fill="darkred")+
  ggtitle("Frequency of Education Level") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Education Level")+
  theme(panel.grid.major.y = element_line(color = "grey",linewidth = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,3000))
```


### Race
```{r}
ggplot(data = subset(Mothership, !is.na(Race_1)),mapping = aes(x = Race_1))+
  geom_bar(color = "black",fill="darkblue")+
  ggtitle("Frequency of Race/Ethnicity") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Race")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,6500))
```

### Gender
```{r}
ggplot(data = subset(Mothership, !is.na(Gender_1)),mapping = aes(x = Gender_1))+
  geom_bar(color = "black",fill="darkorange")+
  ggtitle("Frequency of Gender") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Gender")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  coord_flip()+
  scale_y_continuous(name = "Frequency",limits=c(0,6500))
```


# Pie Chart For Education Status 
We wanted to learn how to make a pie chart in R so here is one!
```{r}
#Create Table and Data Frame
Education<-table(Mothership$Education_1)
Education_df<-as.data.frame(Education)
Education_df

#Rename Columns
colnames(Education_df)[1]="Category"
colnames(Education_df)[2]="Frequency"


Education_df$Category=recode(Education_df$Category,
                             "0"="<Grade 6", 
                             "1"="Grades 7-12",
                             "2"="HS Diploma", 
                             "3"="GED",
                             "4"="Some College",
                             "5"="Associates Degree",
                             "6"="Bachelors Degree",
                             "7"="Some Grad School",
                             "8"="Grad Degree")

ggplot(data = Education_df, mapping = aes(x="", y=Frequency, fill=Category))+
  geom_bar(stat="Identity",width=1,color="white")+
  ggtitle("Education Level of Patients") +
  scale_fill_discrete(name = "Education") +
  coord_polar("y",start=0)+
  theme_void()
```


# Treatment Related Visualizations

## {.tabset}

### Discharge Status
```{r}
### Bar Chart for Discharge Status ###

ggplot(data = subset(Mothership, !is.na(DC_status_1)), mapping = aes(x = DC_status_1))+
  geom_bar(color = "black",fill="darkgreen")+
  ggtitle("Frequency of Treatment Discharge Status") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Discharge Status") +
  theme(panel.grid.major.x = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,6000)) +
  coord_flip()
```

### Treatment Track
```{r}
### Treatment Track ###

ggplot(data = subset(Mothership, !is.na(IPT_track_1)),mapping = aes(x = IPT_track_1))+
  geom_bar(color = "black",fill="skyblue")+
  ggtitle("Frequency of Treatment Type") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Treatment Type")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,6500))
```

### Treatment Year
```{r}
### Treatment Year ###

ggplot(data = subset(Mothership, !is.na(TxYear)),mapping = aes(x = TxYear))+
  geom_bar(color = "black",fill="#9350C7")+
  ggtitle("Frequency of Patients per Year") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Treatment Year")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,1500))
```

### Duration of Treatment
```{r}
### Duration of Treatment ###
ggplot(data = subset(Mothership, !is.na(Duration)),mapping = aes(x = Duration))+
  geom_bar(color = "black",fill="lightgreen")+
  ggtitle("Frequency of Patients per Duration of Treatment") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Treatment Duration")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,6500))

```



