---
title: "Treatment Outcome Visualization"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 1
    #code_folding: hide
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE,warning = FALSE)
getOption("max.print")
# Libraries 
library(tidyverse)
library(dplyr)
library(haven)
library(ggplot2)
library(tidyr)
library("lubridate")

#Data
Mothership<-read.csv("~/Desktop/Coding/data/Mothership_Diag.csv")
Mothership<-mutate(Mothership,
      DC_status_1 = as.factor(DC_status_1),
      Education_1 = as.factor(Education_1),
      Gender_1 = as.factor(Gender_1),
      Relationship_1 = as.factor(Relationship_1),
      Sexuality_1 = as.factor(Sexuality_1),
      IPT_track_1 = as.factor(IPT_track_1),
      Race_1 = as.factor(Race_1),
      Education_1 = as.factor(Education_1),
      Duration = as.factor(Duration),
      )

Mothership$Intake_1<-ymd(Mothership$Intake_1,locale = "en_US.UTF-8")
Mothership$TxYear<-as.numeric(format(Mothership$Intake_1,"%Y"))
Mothership<-mutate(Mothership,
                   TxYear = as.factor(TxYear),
                   TxYear = recode(TxYear,
                                   "1582"="2014",
                                   "2021"="2020",
                                   "2022"="2020"))
```

# Remission from Depression Questionnaire (RDQ)

The following code visualizes the outcomes from the RDQ. The RDQ is broken up into the following categories:

1. Coping Skills: (higher score = more coping skills)
2. Positive Mental Health: (higher score = more positive mental health)
3. Functioning: (higher score = better functioning)
4. Well Being: (higher score = better overall well being)
5. Symptoms: (higher score = more severe depression symptoms)

```{r}
#Read in a New Data Set
Mothership_RDQ<- read_sav("~/Desktop/Coding/data/Mothership_DV.sav")
Mothership_RDQ<-select(Mothership,ID1:Sexuality_1,MDD_C:Day40_CUXOS)
Mothership_RDQ<-data.frame(sapply(Mothership_RDQ,FUN=as.numeric))

#Make This Data Set Long Data
library(tidyr)
Mothership_Long_RDQ <- gather(Mothership_RDQ,rm,RDQ,rdqPRE_coping:rdqPOST_sym,
                              factor_key = "T")
Mothership_Long_RDQ <- Mothership_Long_RDQ[order(Mothership_Long_RDQ$ID1),]

#Create a Time Variable
Mothership_Long_RDQ$PrePost <- NA
Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPRE_coping"]<-"Pre"
Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPRE_pmh"]<-"Pre"
Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPRE_func"]<-"Pre"
Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPRE_wbs"]<-"Pre"
Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPRE_sym"]<-"Pre"
Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPOST_coping"]<-"Post"
Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPOST_pmh"]<-"Post"
Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPOST_func"]<-"Post"
Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPOST_wbs"]<-"Post"
Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPOST_sym"]<-"Post"



#Create a New Data Set with an Average Depression Variable and Race
Mothership_Mean_RDQ<-Mothership_Long_RDQ %>%
  group_by(rm,PrePost) %>%
  summarise(RDQ=mean(RDQ,na.rm=TRUE))

#Add a Paired Variable to the New Data Set
Mothership_Mean_RDQ<-mutate(Mothership_Mean_RDQ,
                            paired=case_when(rm=="rdqPRE_coping"~"1",
                                             rm=="rdqPOST_coping"~"1",
                                             rm=="rdqPRE_pmh"~"2",
                                             rm=="rdqPOST_pmh"~"2",
                                             rm=="rdqPRE_func"~"3",
                                             rm=="rdqPOST_func"~"3",
                                             rm=="rdqPRE_wbs"~"4",
                                             rm=="rdqPOST_wbs"~"4",
                                             rm=="rdqPRE_sym"~"5",
                                             rm=="rdqPOST_sym"~"5"))

Mothership_Mean_RDQ

str(Mothership_Mean_RDQ$rm)

#Pre Post RDQ Plot - combined 
ggplot(data=Mothership_Mean_RDQ,
       aes(x=factor(PrePost,level=c("Pre","Post")),y=RDQ,
           group=rm,color=paired,!is.na(PrePost)))+
  geom_point(size=2.5)+
  geom_line(group=Mothership_Mean_RDQ$paired,size=1.5)+
  scale_x_discrete(name="Time Point")+
  scale_y_continuous(name="RDQ Subscore")+
  ggtitle("Mean Pre and Post Scores of the Remission from Depression Questionnaire")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title = element_blank())+
  scale_color_manual(values=c("1"="#8956BB","2"="#4C4452","3"="#B1A8B9",
                               "4"="#00BCA3","5"="#008570"),
                     labels=c("Coping Skills","Positive Mental Health",
                              "Functioning","Well-Being","Symptoms")) 



# pre post RDQ Plot - facet wrap
ggplot(data=Mothership_Mean_RDQ,
       aes(x=factor(PrePost,level=c("Pre","Post")),y=RDQ,
           group=rm,color=paired,!is.na(PrePost))) +
  geom_point(size=2.5) +
  geom_line(group=Mothership_Mean_RDQ$paired,size=1.5) +
  scale_x_discrete(name="Time Point") +
  scale_y_continuous(name="RDQ Subscore",limits = c(0, 40)) +
  ggtitle("Mean Pre and Post Scores of the Remission from Depression Questionnaire") +
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2)) +
  theme(panel.background=NULL) +
  theme(legend.position="none") +
  scale_color_manual(values=c("1"="#8956BB","2"="#4C4452","3"="#B1A8B9",
                               "4"="#00BCA3","5"="#008570")) +
  facet_wrap(~paired, labeller = labeller(paired =
    c("1" = "Coping Skills",
      "2"="Positive Mental Health",
      "3"="Functioning",
      "4"="Well-Being",
      "5"="Symptoms")))
```


# Pre and Post Scores

## {.tabset}

### Extract pre/post scores
```{r}
#1. load DF

Mothership
    
    Mothership_post <- Mothership |>
        filter(
          is.na(Prev_AdmitID_1),
          C_Admit_1 == 1
          ) |>
        mutate(
          dummy = -99
        )

    # Depressiopn
    CUDOS_Score_post <-  select(Mothership_post, dummy,Day1_CUDOS:Day40_CUDOS)
    # Anxiety
    CUXOS_Score_post <- select(Mothership_post, dummy,Day1_CUXOS:Day40_CUXOS)


#2. Getting post scores for people who have NA for post
    
    # Depression
    Post_DEP <- NA
    PD_df <- NA
    for(i in 1:nrow(CUDOS_Score_post)){
    PD_df <- unname(unlist(CUDOS_Score_post[i,]))
    PD_df <- PD_df[!is.na(PD_df)]
    PD_df <- tail(PD_df, n=1)
    Post_DEP <- rbind(Post_DEP,PD_df)
    }
    Post_DEP
    Post_Dep <- Post_DEP[-1]

    # Anxiety
    Post_ANX <- NA
    PA_df <- NA
    for(i in 1:nrow(CUXOS_Score_post)){
    PA_df <- unname(unlist(CUXOS_Score_post[i,]))
    PA_df <- PA_df[!is.na(PA_df)]
    PA_df <- tail(PA_df, n=1)
    Post_ANX <- rbind(Post_ANX,PA_df)
    }
    
    Post_ANX
    Post_anx <- Post_ANX[-1]

# 3. Getting BL scores for people who have NA at Baseline 
  
    # Depression / Anxiety Dummy variable
    CUDOS_Score_pre <-  select(Mothership_post, Day1_CUDOS:Day40_CUDOS,dummy)
    CUXOS_Score_pre <- select(Mothership_post, Day1_CUXOS:Day40_CUXOS,dummy)

    # Depression
    Pre_DEP <- NA
    PD_df <- NA
    for(i in 1:nrow(CUDOS_Score_pre)){
    PD_df <- unname(unlist(CUDOS_Score_pre[i,]))
    PD_df <- PD_df[!is.na(PD_df)]
    PD_df <- head(PD_df, n=1)
    Pre_DEP <- rbind(Pre_DEP,PD_df)
    }
    Pre_dep <- Pre_DEP[-1]

    # Anxiety
    Pre_ANX <- NA
    PA_df <- NA
    for(i in 1:nrow(CUXOS_Score_pre)){
    PA_df <- unname(unlist(CUXOS_Score_pre[i,]))
    PA_df <- PA_df[!is.na(PA_df)]
    PA_df <- head(PA_df, n=1)
    Pre_ANX <- rbind(Pre_ANX,PA_df)
    }
    Pre_anx <- Pre_ANX[-1]

#4 Adding it back to mother ship
    Mothership_post <- Mothership_post |>
      mutate(
        CUDOS_pre = ifelse(is.na(BL_CUDOS),Pre_dep,BL_CUDOS),
          CUDOS_pre = ifelse(CUDOS_pre < 0, NA, CUDOS_pre),
        CUXOS_pre = ifelse(is.na(BL_CUXOS),Pre_anx,BL_CUXOS),
          CUXOS_pre = ifelse(CUXOS_pre < 0, NA, CUXOS_pre),
        CUDOS_post = ifelse(Post_Dep < 0, NA, Post_Dep),
        CUXOS_post = ifelse(Post_anx < 0, NA, Post_anx)
      )
    

#7. create new DF with Varaibles we want

AnxDep_PrePost <- data.frame(cbind(Mothership_post$ID1,
                                  Mothership_post$Disorder_Type,
                                  Mothership_post$CUDOS_pre,
                                  Mothership_post$CUDOS_post,
                                  Mothership_post$CUXOS_pre,
                                  Mothership_post$CUXOS_post)) %>%
  filter(!is.na(Mothership_post$Disorder_Type))

colnames(AnxDep_PrePost) = c("ID1","Disorder_Type", "CUDOS_pre","CUDOS_post","CUXOS_pre","CUXOS_post")

#8. Create long data frame

AnxDep_PrePost_Long <- AnxDep_PrePost %>% 
  pivot_longer(
    cols = CUDOS_pre:CUXOS_post, 
    names_to = "Test",
    values_to = "Score"
  )
AnxDep_PrePost_Long <-AnxDep_PrePost_Long %>%
  mutate(
    PrePost = ifelse(
      Test == "CUDOS_pre", "Pre",
      ifelse(Test == "CUXOS_pre" , "Pre", "Post"
    )),
    Score = as.integer(Score),
    Test = as.factor(Test),
    Test = as.factor(ifelse(Test == "CUDOS_pre",  "CUDOS",
                     ifelse(Test == "CUDOS_post", "CUDOS", "CUXOS"
                     ))))  
           
#9. Convert to data frame with means of values to be plotted
AnxDep_PrePost_mean<-AnxDep_PrePost_Long %>%
  group_by(Test,PrePost) %>%
  summarise(Score=mean(Score,na.rm=TRUE))


```

### Overall Plot
```{r}
# Pre Post CUDOS/CUXOS Plot
ggplot(data=AnxDep_PrePost_mean,
       aes(x=factor(PrePost,level=c("Pre","Post")),y=Score,
           group=Test,color=Test))+
  geom_point(size=2.5)+
  geom_line(group=AnxDep_PrePost_mean$PrePost,size=1.5)+
  scale_x_discrete(name="Time Point")+
  scale_y_continuous(name="CUDOS/CUXOS Score")+
  ggtitle("Mean Pre and Post Scores of the Anxiety and Depression")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title = element_blank())

```


### Line Plot By Disorder
```{r}
#1. Creaate new datasets with only anxiety / depresssion

ANX_PrePost<- AnxDep_PrePost_Long %>%
  filter(Test == "CUXOS")

DEP_PrePost<- AnxDep_PrePost_Long %>%
  filter(Test == "CUDOS")


#2. Create DF grouped buy disorder type
ANX_PrePost_mean<-ANX_PrePost %>%
  group_by(Disorder_Type,PrePost) %>%
  summarise(Score=mean(Score,na.rm=TRUE))

DEP_PrePost_mean<-DEP_PrePost %>%
  group_by(Disorder_Type,PrePost) %>%
  summarise(Score=mean(Score,na.rm=TRUE))

#### ANX
ggplot(data=ANX_PrePost_mean,
       aes(x=factor(PrePost,level=c("Pre","Post")),y=Score,
           group=Disorder_Type,color=Disorder_Type))+
  geom_point(size=2.5)+
  geom_line(size=1)+
  scale_x_discrete(name="Time Point")+
  scale_y_continuous(name="CUXOS Score")+
  labs(title = "Mean Pre and Post Anxiety Scores By Disorder Type",
       subtitle = "Self Report anxiety was assessed using the CUXOS",
       caption = "Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-40 (moderate), 41+ (severe)")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title = element_blank()) 

#### DEP
ggplot(data=DEP_PrePost_mean,
       aes(x=factor(PrePost,level=c("Pre","Post")),y=Score,
           group=Disorder_Type,color=Disorder_Type))+
  geom_point(size=2.5)+
  geom_line(size=1)+
  scale_x_discrete(name="Time Point")+
  scale_y_continuous(name="CUDOS Score")+
  labs(title = "Mean Pre and Post Depression Scores By Disorder Type",
       subtitle = "Self report depression was assessed using the CUDOS",
       caption = "Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-45 (moderate), 46+ (severe)")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title = element_blank())
```

### Dumbell Plot by Disorder
```{r}
Pre_ANX<-ANX_PrePost_mean %>%
  filter(PrePost == "Pre")

Post_ANX<-ANX_PrePost_mean %>%
  filter(PrePost == "Post")

Plot_Text<- dplyr::count(ANX_PrePost, Disorder_Type)
Plot_Text

"#aeb6bf"


ggplot(data=Pre_ANX,
       aes(x=Disorder_Type,y=Score,
           group=Disorder_Type,color=Disorder_Type))+
  geom_segment(aes(x=Disorder_Type, xend=Post_ANX$Disorder_Type, y=Score, yend=Post_ANX$Score),color = "#ad3e4f",
              size = 4, #Note that I sized the segment to fit the points
              alpha = .5) +
  geom_point( aes(x=Disorder_Type, y=Score), color= "#F90000", size=3.5) +
  geom_point( aes(x=Post_ANX$Disorder_Type, y=Post_ANX$Score), color= "#0CC541", size=3.5) +
  labs(title = "Mean Pre and Post Anxiety Scores By Disorder Type",
       subtitle = "Self Report anxiety was assessed using the CUXOS",
       caption = "Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-40 (moderate), 41+ (severe)")+
  scale_y_reverse(limits = c(45,15)) +
  coord_flip() +
  theme_classic()+
  theme(#legend.position = "none",
         plot.background = element_rect(
      fill = "white",
      colour = "white"))
  
#sum(as.factor(ANX_PrePost$Disorder_Type))

  
Pre_DEP<-DEP_PrePost_mean %>%
  filter(PrePost == "Pre")

Post_DEP<-DEP_PrePost_mean %>%
  filter(PrePost == "Post")

ggplot(data=Pre_DEP,
       aes(x=Disorder_Type,y=Score,
           group=Disorder_Type,color=Disorder_Type))+
  geom_segment(aes(x=Disorder_Type, xend=Post_DEP$Disorder_Type, y=Score, yend=Post_DEP$Score),color = "#4068a8",
              size = 4, #Note that I sized the segment to fit the points
              alpha = .5) +
  geom_point( aes(x=Disorder_Type, y=Score), color= "#F90000", size=3.5) +
  geom_point( aes(x=Post_DEP$Disorder_Type, y=Post_DEP$Score), color= "#0CC541", size=3.5) +
  labs(title = "Mean Pre and Post Depression Scores By Disorder Type",
       subtitle = "Self Report anxiety was assessed using the CUDOS",
       caption = "Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-45 (moderate), 46+ (severe)",
       ylab = "Disorder Type")+
  scale_y_reverse(limits = c(45,15)) +
  coord_flip() +
  theme_classic()+
  theme(#legend.position = "none",
         plot.background = element_rect(
      fill = "white",
      colour = "white"))
```



